---
title: "R Notebook"
output: html_notebook
---

```{r}
set.seed(1234)
library(dplyr)
library(expm)
library(irlba)
library(ggplot2)
library(purrr)
library(lfboot)
source("visualization_functions.R")
theme_set(min_theme())
```
```{r}
B <- 1000
N <- 1000
D <- 100
K <- 2
U <- r_ortho(N, D)
V <- r_ortho(D, D)
Sigma <- c(rep(100, 2), rep(0.0, D - K))
X <- U %*% diag(Sigma) %*% t(V) + rmat(N, D, 0.1)
beta <- c(c(1, -1), rep(0, D - K))
y <- U %*% diag(sqrt(Sigma)) %*% beta + rnorm(N, 0, .1)
```

Here is the strategy that extracts the features once and then applies a
parametric bootstrap according to the assumed model.

```{r}
f <- features(X)
boot_fun <- param_boot(f(X), K)
ud_hats <- rerun(B, boot_fun()$ub) %>%
  align_to_list(df = F)
ud_combined <- align_with_truth(ud_hats, U, Sigma) %>%
  left_join(data.frame(i = seq_along(y), y = y))
```

```{r}
plot_facets(ud_combined)
plot_facets(ud_combined, facet = FALSE)
#ggsave("~/Desktop/l_approach1_facet.png", dpi = 250)
plot_overlay(ud_combined, max_i = 100)
#ggsave("~/Desktop/l_approach1.png", dpi = 250)
```


```{r}
contained <- coverage(ud_combined %>% filter(b < B + 1),  ud_combined %>% filter(b == B + 1))
mean(contained)
```

What if we instead extract $B$ sets of features?

```{r}
f <- features(X)
Zb <- rerun(B, {
  full_features <- f(X)
  svf <- irlba(full_features, nv=K) 
  svf$u %*% diag(svf$d)
})
ud_hats <- align_to_list(Zb)
ud_combined <- align_with_truth(ud_hats, U, Sigma) %>%
  left_join(data.frame(i = seq_along(y), y = y))
```

```{r}
contained <- coverage(ud_combined %>% filter(b < max(b)),  ud_combined %>% filter(b == max(b)))
mean(contained)
```

```{r}
plot_facets(ud_combined)
#ggsave("~/Desktop/l_approach2_facet.png", dpi = 250)
plot_overlay(ud_combined, 100)
#ggsave("~/Desktop/l_approach2.png", dpi = 250)
```

Here is a kind of compromise between repeated feature learning and a parametric
bootstrap. The simulated samples are somewhat complicated (projected mixtures,
it seems like). But it is computationally simpler and does seem more honest than
not using any feature relearning.

```{r}
f <- features(X)
Zb <- rerun(100, f(X))
boot_fun <- param_boot_ft(Zb)
ud_hats <- rerun(B, boot_fun()$ub) %>%
  align_to_list()
ud_combined <- align_with_truth(ud_hats, U, Sigma) %>%
  left_join(data.frame(i = seq_along(y), y = y))
```

```{r}
plot_facets(ud_combined)
#ggsave("~/Desktop/l_approach3_facet.png", dpi = 250)
plot_overlay(ud_combined, 100)
#ggsave("~/Desktop/l_approach3.png", dpi = 250)
```
```{r}
contained <- coverage(ud_combined %>% filter(b < max(b)),  ud_combined %>% filter(b == max(b)))
mean(contained)
```

