---
title: "R Notebook"
output: html_notebook
---

```{r}
set.seed(1234)
library(dplyr)
library(ggplot2)
library(purrr)
library(lfboot)
theme_set(min_theme())
```
Here are some helper visualizations used in this script but unlikely to be
generally useful.

```{r}
align_to_list <- function(Zb, df = F, tol = 0.05) {
  procrustes(Zb, tol = tol) %>%
    .[["x_align"]] %>%
    arr_to_list(df = df)
}

align_with_truth <- function(ud_hats, U, Sigma, tol = 0.05) {
  c(ud_hats, list(U %*% diag(sqrt(Sigma)))) %>%
    align_to_list(tol = tol, df = T) %>%
    bind_rows(.id = "b") %>%
    group_by(b) %>%
    mutate(i = row_number()) %>%
    ungroup() %>%
    mutate(b = as.integer(b))
}
```


```{r}
B <- 1000
N <- 200
D <- 50
K <- 2
U <- r_ortho(N, D)
V <- r_ortho(D, D)
Sigma <- c(rep(10, 2), rep(0.01, D - K))
X <- U %*% diag(Sigma) %*% t(V) + rmat(N, D, 0.01)
```

Here is the strategy that extracts the features once and then applies a
parametric bootstrap according to the assumed model.

```{r}
f <- features(X)
boot_fun <- param_boot(f(X), K)
ud_hats <- rerun(B, boot_fun()$ub) %>%
  align_to_list(df = F)
ud_combined <- align_with_truth(ud_hats, U, Sigma)
```

```{r}
contained <- coverage(ud_combined %>% filter(b < B + 1),  ud_combined %>% filter(b == B + 1))
mean(contained)
```

What if we instead extract $B$ sets of features?

```{r}
f <- features(X)
Zb <- rerun(B, f(X))
ud_hats <- align_to_list(Zb)
ud_combined <- align_with_truth(ud_hats, U, Sigma)
```

```{r}
contained <- coverage(ud_combined %>% filter(b < B + 1),  ud_combined %>% filter(b == B + 1))
mean(contained)
```

Here is a kind of compromise between repeated feature learning and a parametric
bootstrap. The simulated samples are somewhat complicated (projected mixtures,
it seems like). But it is computationally simpler and does seem more honest than
not using any feature relearning.

```{r}
f <- features(X)
Zb <- rerun(10, f(X))
boot_fun <- param_boot_ft(Zb, K)
ud_hats <- rerun(B, boot_fun()$ub) %>%
  align_to_list()
ud_combined <- align_with_truth(ud_hats, U, Sigma)
```
