---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(ggplot2)
library(purrr)
library(lfboot)
theme_set(min_theme())
```

```{r}
N <- 200
D <- 50
K <- 2
U <- r_ortho(N, D)
V <- r_ortho(D, D)
Sigma <- c(rep(10, 2), rep(0.01, D - K))
X <- U %*% diag(Sigma) %*% t(V) + rmat(N, D, 0.01)
```

If we use an unsupervised feature extractor, there is no problem.

```{r}
y <- rnorm(N)
f <- features(X)
summary(lm(y ~ f(X)))
```


When we don't split the data, the extracted features incorrectly look related to
the response.

```{r}
library(broom)
library(tidyr)
p_vals <- list()
for (i in seq_len(1000)) {
  y <- rnorm(N)
  fy <- supervised_features(X, y)
  p_vals[[i]] <- tidy(summary(lm(y ~ -1 + fy(X))))
}
```


```{r, fig.width = 4, fig.height = 2}
ggplot(bind_rows(p_vals)) +
  geom_histogram(aes(p.value)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0, .1, 0)) +
  facet_wrap(~ term)
#ggsave("~/Desktop/bias_beta_0.png", dpi = 200)
```

If we split, then we can see the difference clearly.

```{r}
y <- rnorm(N)
ix <- 1:(N / 2)
fy <- supervised_features(X[ix, ], y[ix])
summary(lm(y[-ix] ~ fy(X[-ix, ])))
```

What if there were actually a relationship between the underlying features and
the response? We can still detect the difference.

```{r}
beta <- c(1.8, -1.8, rep(0, D - 2))
y <- U %*% diag(sqrt(Sigma)) %*% beta + rnorm(N)
ix <- 1:(N / 2)
fy <- supervised_features(X[ix, ], y[ix]) # the "Z"s
summary(lm(y[-ix] ~ fy(X[-ix, ])))
```

Of course, this is only calling the feature extractor once. We'll need to call
it $B$ times in order to be able to evaluate feature stability. The inference
will be on the consensus Z's.