---
title: "Visualize Learned Features"
output: html_notebook
params:
  output_path: "/Users/kris/Downloads/figs/"
  tiles_dir: "/Users/kris/Documents/stability_data"
---

This notebook includes helpers for visualizing the learned aligned features
$\mathbf{Z}_{b}$.

```{r}
library("ggplot2")
library("readr")
library("inference")
library("dplyr")
library("purrr")
library("stringr")
library("gridExtra")
theme_set(theme_bw())
dpath <- function(s, d=params$output_path) {
  file.path(d, s)
}
```

First, read in all the aligned features, their centroids, and edges between
features and centroids.

```{r}
# directory containing unzipped figure results
epaths <- dir(params$output_path, "edge_data_*", recursive = TRUE, full = TRUE) 
cpaths <- dir(params$output_path, "centroids_*", recursive = TRUE, full = TRUE)
```

```{r}
edge_data <- epaths %>%
  map_dfr(read_csv, col_types = cols(), .id = "path") %>%
  mutate(path = as.integer(path))
edge_data$method <- str_extract(epaths, "cnn|rcf|vae")[edge_data$path] %>%
  toupper()
edge_data$train_perc <- str_extract(epaths, "15|50|90")[edge_data$path]
edge_data$sca <- str_extract(epaths, "svd|sca")[edge_data$path] %>%
  toupper()
centroids <- cpaths %>%
  map_dfr(read_csv, col_types = cols(), .id = "path") %>%
  mutate(path = as.integer(path))
centroids$method <- str_extract(cpaths, "cnn|rcf|vae")[centroids$path] %>%
  toupper()
centroids$train_perc <- str_extract(epaths, "15|50|90")[centroids$path]
centroids$sca <- str_extract(epaths, "svd|sca")[centroids$path] %>%
  toupper()

paths <- sapply(centroids$rel_path, dpath, d = params$tiles_dir)
j1 <- 2
j2 <- 1
```

Overlay example patches on the observed coordinates.

```{r}
cur_cols <- paste0("meandim", c(j1, j2))
for (perc in c("15", "50", "90")) {
  for (dimred in c("SCA", "SVD")) {
    
    p <- list()
    for (m in c("CNN", "RCF", "VAE")) {
      coords <- centroids %>%
        filter(
          split == "test",
          method == m,
          train_perc == perc,
          sca == dimred
        ) %>%
        select(one_of(cur_cols))
      colnames(coords) <- c("x", "y")
      
      imsize <- diff(range(coords$y)) / 14.5
      p[[m]] <- image_grid(coords, paths, min_dist = 1, density = c(12, 14), imsize = imsize) +
        labs(
          x = sprintf("Learned Feature %s", j1),
          y = sprintf("Learned Feature %s", j2)
        ) +
        scale_fill_manual(values = c("red", "green", "blue")) +
        theme(panel.grid.minor = element_blank())
    }
    
    ga <- grid.arrange( p[[1]] + ggtitle("CNN"), p[[2]] + ggtitle("RCF"), p[[3]] + ggtitle("VAE"), ncol = 2 )
    ggsave(
      sprintf("~/Desktop/conceptual/learned_inference/notes/figure/sim_imagegrid-%s-%s-1-2.png", dimred, perc),
      ga, dpi = 500, width = 9, height = 10
    )
  }
}
```

```{r, fig.height = 10, fig.width = 10}
```

Consider the original discrepancies between features and their centroids.

```{r, fig.height = 10, fig.width = 8}
edge_data_ <- edge_data %>%
  filter(sca == "SCA") %>%
  split(.$method, .$train_perc) %>%
  map_dfr(~ .x %>% filter(rel_path %in% unique(.x$rel_path)[1:400])) %>%
  mutate(split = factor(split, levels = c("train", "dev", "test")))

centroids <- centroids %>%
  mutate(split = factor(split, levels = c("train", "dev", "test"))) %>%
  filter(sca == "SCA")

ggplot(edge_data_) +
  geom_point(
    aes_string(x = paste0("dim", j1), y = paste0("dim", j2), col = "y", shape = "split"),
    alpha = 0.2, size = 0.4
  ) +
  geom_segment(
    aes_string(x = paste0("meandim", j1), xend = paste0("dim", j1), y = paste0("meandim", j2), yend = paste0("dim", j2), col = "y"),
    size = 0.1, alpha = 0.8
  ) +
  geom_point(
    data = centroids %>% filter(rel_path %in% edge_data_$rel_path),
    aes_string(x = paste0("meandim", j1), y = paste0("meandim", j2), col = "y", shape = "split"),
    alpha = .8, size = 0.6
    ) +
  facet_wrap(method ~ train_perc, scale = "free") +
  scale_color_viridis_c() +
  guides(shape = guide_legend(override.aes = list(size = 2))) +
  labs(x = sprintf("Learned Feature %s", j1), y = sprintf("Learned Feature %s", j2)) +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 6),
    axis.ticks = element_blank()
  )
ggsave("~/Desktop/conceptual/learned_inference/notes/figure/embeddings-sca-1-2.png", dpi = 500)
```
And place into context by showing all samples in one figure.

```{r}
cpaths
centroids %>% filter(split == "test", train_perc == "50")
```

```{r, fig.height = 10, fig.width = 7.5}
ggplot(centroids %>% filter(sca == "SVD")) +
  geom_point(
    aes_string(x = paste0("meandim", j1), y = paste0("meandim", j2), col = "y", shape = "split"),
    alpha = .9, size = 1.5 
    ) +
  facet_wrap(method ~ train_perc, scale = "free") +
  scale_color_viridis_c() +
  labs(x = sprintf("Learned Feature %s", j1), y = sprintf("Learned Feature %s", j2)) +
  theme(legend.position = "bottom")
ggsave("~/Desktop/conceptual/learned_inference/notes/figure/embeddings-svd-1-2.png", dpi = 500)
```
