
\section{Context}

We briefly summarize the methods used in this work.


\subsubsection{Stability}

Many statistical algorithms revolve around the idea that meaningful conclusions should be stable to perturbations \cite{yu2013stability}. In this work, we make use of stability selection, a technique for evaluating significance in high-dimensional linear models \cite{meinshausen2010stability}.

For a dataset $\mathbf{X}\in \reals^{n \times p}$ and $\mathbf{y} \in
\reals^{n}$, stability selection proceeds as follows. First, $B$ subsamples of
size $\lfloor \frac{n}{2} \rfloor$ are drawn from the data, and for each a lasso
regression is run over a grid of $\lambda$ regularization parameters. Each of
these regressions results in $p$ coefficient trajectories, and important
features will generally become nonzero earlier on the regularization path (that
is, even with large regularization $\lambda$). For a given $\lambda$ and feature
$j$, let $\hat{\Pi}_{j}\left(\lambda\right)$ measure the fraction of subsamples
that had nonzero $\hat{\beta}_j\left(\lambda\right)$. The paths
$\left(\hat{\Pi}_{j}\lambda\left(\lambda\right)\right)_{j = 1}^{p}$summarize the
importance of the $p$ regression features. For a given stringency threshold
$\pi_{thr}$, the procedure selects features $\hat{S} = \{j : \max_{\lambda}
\hat{\Pi}_{j}\left(\lambda\right) \geq \pi_{thr}\}$.

Let $q_{\Lambda} = \Eabsarg{\hat{S}_{\Lambda}}$ denote the expected number of
selected features. It can be shown that, assuming some conditions on the
selection procedure $\hat{S}$, and requiring a stringency $\pi_{thr} \geq
\frac{1}{2}$, the expected number of falsely selected features is bounded by
$\frac{1}{2\pi_{thr} - 1} \frac{q_{\Lambda}^2}{p}$. The term
$\frac{q_{\Lambda}^2}{p}$ is like the typical fraction of selected features; the
coefficient $\frac{q_{\Lambda}}{2\pi_{thr} - 1}$ describes the fraction of those
that are expected to be false positives.

\subsubsection{Feature Learning}

(tk: do I need to define activation?)

In this work, we will examine the behavior of three particular feature learning algorithms. The first approach is called the Variational Autoencoder (VAE). Like principal components analysis, this algorithm learns a $K$-dimensional reduction of a dataset by optimizing a reconstruction objective. Formally, the algorithm first posits some generative model $p\left(z\right)p_{\xi}\left(x \vert z\right)$ of the data; $p\left(z\right)$ is a prior on latent features and $p_{\xi}\left(x \vert x\right)$ is a likelihood parameterized by $\xi$. The algorithm finds a pair $\xi, \varphi$ maximizing the lower bound,

\begin{align*}
\log p_{\xi}\left(x\right) \geq  \mathbb{E}_{q_{\varphi}}\left[\log p]_{\xi}(x \mid z)\right]-D_{KL}\left(q_{\varphi}(z \mid x) \| p(z)\right)
\end{align*}

where $q_{\varphi}\left(z \vert x\right) = N\left(\mu_{\varphi}\left(x\right), \sigma^{2}_{\varphi}\left(x\right)\right)$ maps raw data examples to distributions in a latent space of more meaningful features. This optimization problem is nonconvex, and is typically solved through a variant of stochastic gradient descent.

Second, we investigate features learned in a supervised way through a
Convolutional Neural Network (CNN). For regression, a CNN optimizes the
empirical estimate of the risk $\mathbf{E}\|y -
f_{W_{1:L}}\left(x\right)^{T}\beta\|_{2}^{2}$ over $W_{1:L}$ and $\beta$. Here,
$f_{W_{1:L}}$ transforms the raw input into the ``last layer''’s features, and
is defined recursively according to

\begin{align*}
f^{l}_{W_{1:l}}\left(x\right) &= \sigma\left(W_{l}f^{l - 1}_{W\_{1:(l - 1)}}\left(x\right)\right)\\
f^{0}\left(x\right) &= x
\end{align*}

for $\sigma\left(x\right)$ defined as $\sigma\left(x\right) := x \indic{x \geq
  0}$ and matrices $W$ restricted to the set of convolution operators. Like in
the VAE, this optimization is nonconvex and is typically found through
first-order optimization methods.

Third, we consider a random convolutional features (RCF) model. Here, a random
sample of $P$ training examples $x_{i_1}, \dots, x_{i_P} \in \reals^{w \times h
  \times c}$ are selected; we are assuming the $x_{i}$ are $c$-channel images
with dimension $w\times h$. For each sample, a random $s \times s$ patch is
extracted; call the collection $w_{1}, \dots, w_{p} \in \reals^{s \times s
  \times c}$. For any $c$-channel image $x$, the $p^{th}$ feature $z$ is found
by convolving $x$ with $w_{p}$ and averaging over all the associated
coordinates.

To train an RCF, the training data are first featurized into $\mathbf{Z} \in
\reals^{n \times P}$ using random image patches, as described above. Then, a
ridge regression model is trained, solving

\begin{align*}
\hat{\beta} := \arg \min_{\beta} \|y - \mathbf{Z}\beta\|_{2}^{2} + \lambda \|\beta\|_{2}
\end{align*}

For a new example $x^{\ast}$, the same image patches $w_{1}, \dots, w_{p}$ are used to create a featurization $z^{\ast}$, and predictions are made with $z^{\ast T}\hat{\beta}$. Unlike either the VAE or CNN, this model does not require gradient based training, and it can serve as a fast (and often effective) baseline.

\subsubsection{Procrustes Analysis}
Procrustes Analysis gives a way of aligning multiple tables. Given two tables $\mathbf{X}$ and $\mathbf{Y}$, the Procrustes problem finds the rotation matrix $\mathbf{R}$ solving the optimization,

\begin{align*}
\min_{\mathbf{R} \mathcal{O}} \|\mathbf{X} - \mathbf{Y}\mathbf{R}\|^{2}_{2},
\end{align*}

where $\mathcal{O}$ denotes the space of orthogonal matrices. Using the associated Lagrangian,

\begin{align*}
\max_{\mathbf{R}, \mathbf{\Lambda} \succ 0} \|\mathbf{X} - \mathbf{Y}\|_{2}^{2} - \mathbf{\Lambda}\left(\mathbf{R}^{T}\mathbf{R} - \mathbf{I}\right)
\end{align*}

the solution can be shown to be $\hat{\mathbf{R}} = \mathbf{U}^{T}\mathbf{V}$ for $\mathbf{U}$ and $\mathbf{V}$ obtained by the SVD of $\mathbf{X}^{T}\mathbf{Y}$. More generally, for $B$ matrices $\mathbf{X}_{1}, \dots, \mathbf{X}_{B}$, the generalized procrustes problem finds $B$ rotations $\mathbf{R}_{1}, \dots, \mathbf{R}_{B}$ and mean matrix $\mathbf{M}$ solving

\begin{align*}
\min_{\mathbf{R}_{1}, \dots, \mathbf{R}_{B} \in \mathcal{O}, M} \sum_{b = 1}^{B} \|\mathbf{X}_{b}\mathbf{R}_{b} - \mathbf{M}\|_{2}^{2}.
\end{align*}

While there is no closed form solution, the optimization can be solved by cyclically updating each $\mathbf{R}_{b}$ via standard Procrustes problems and then updating $\mathbf{M} = \frac{1}{B} \sum_{b = 1}^{B} \mathbf{X}_{b} \mathbf{R}_{b}$.

\subsubsection{Representation Analysis}

Our approach is closely related to methods for representation analysis, which
compare activations across deep learning models. One popular approach to
representation analysis is Singular Vector CCA (SVCCA). This method can be used
to compare pairs of representations, coming from different layers, models, or
training epochs, for example. In SVCCA, the two representations are identified
with two matrices, $X \in \reals^{n \times k_{1}}$ and $Y \in \reals^{n \times
  k_{2}}$. The $ij^{th}$ cell in each matrix corresponds to the activation of
neuron $j$ on sample $i$. Each representation effectively corresponds to a
pattern of activations across a collection of neurons.

To compare these representations, SVCCA first computes singular value
decompositions $X = U_{X}D_{X}V_{X}^{T}$ and $Y = U_{Y}D_{Y}V_{T}^{T}$. The
coordinates of these matrices with respect to the top $K$ singular vector
directions are then extracted, $Z_{X} = U_{X, 1:K}D_{X, 1:K}$ and $Z_{Y} = U_{Y,
  1:K}D_{Y, 1:K}$. Finally, a canonical correlation analysis is performed on
these coordinate matrices. That is, the top CCA directions $u_{1}, v_{1}$ are
found by optimizing

\begin{align*}
  \text{maximize }& u^{T}\hat{\Sigma}_{Z_{X}}^{-\frac{1}{2}}\hat{\Sigma}_{Z_{X}Z_{Y}}\hat{\Sigma}_{Z_{Y}}^{-\frac{1}{2}}v \\
  \text{such that } & \|u\|_{2} = \|v\| = 1
\end{align*}

and subsequent directions are found by solving the same problem, after
orthogonalizing $Z_{X}$ and $Z_{Y}$ to previously extracted directions. The
value of the objective for each of the $K$ directions extracted is denoted
$\rho_{k}$, and the overall similarity between the two representations is taken
to be the average of these canonical correlations: $\frac{1}{K}\sum_{k = 1}^{K}
\rho_{k}$.

Note that, while in principle, it would be possible to perform a CCA on the
activations $X$ and $Y$ directly, for representations with many neurons, the
dimensionality reduction step can lead to dramatic performance gains, because it
avoids inverting a high-dimensional correlation matrix.

\subsection{Sparse Components Analysis}

Like SVCCA, we reduce dimensionality of our learned features before comparing
them. We reductions using both PCA and a recently proposed variant called Sparse
Components Analysis (SCA). For a given data matrix $X$ and a number of
components $K$, and sparsity parameter $\gamma$, SCA solves the optimization

\begin{align*}
  \text{maximize }_{Z, B, Y} &\|X - Z B Y^{T}\|_{F} \\
  \text{such that }Z \in &\mathcal{O}\left(n, K\right) \\
  Y \in &\mathcal{O}\left(p, k\right) \\
  \|Y\|_{1} \leq \gamma.
\end{align*}

Here, $\mathcal{O}\left(m, n\right)$ corresponds to the space of $m \times n$
orthogonal matrices. The matrix $Y$ provides the $K$ the SCA loadings, and the
product $ZB$ provide the coordinates of each sample with respect to that basis.
Note that if $B$ is forced to be diagonal, then this optimization reduces to
previously proposed versions of sparse PCA (we work with nondiagonal $B$
throughout this work). This optimization does not directly provide an ordering
of the loadings. However, the proportion of variance explained by each dimension
can still be computed, and this can be indirectly used to order the dimensions.
